Solutions to Integer Programming from Quantum Annealing

### 2020-05-11 paper/main.tex
Reshuffle adjustments

-\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography]{revtex4}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{bm,bbm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{dsfont}

@@

@@

@@

%----------------------------------------------------------------------------------------
\subsection{QUBO}
\label{sec:methods:qubo}
%----------------------------------------------------------------------------------------

@@

@@

%----------------------------------------------------------------------------------------
\subsection{Application to the Dominating Set Problem}
\label{sec:methods:mds}
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
\subsubsection{Minimum Dominating Set}
%----------------------------------------------------------------------------------------

@@

@@

%----------------------------------------------------------------------------------------
\subsection{Simulation Details}
%----------------------------------------------------------------------------------------

@@

@@

...

>>>>

\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography]{revtex4}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{bm,bbm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{dsfont}

@@

% disable subsections and subsubsections in the TOC
\makeatletter
\def\l@subsubsection#1#2{}
\makeatother

@@

%----------------------------------------------------------------------------------------
\subsubsection{Slack variables}
\label{sec:methods:slack}
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
\subsubsection{Bit basis}
\label{sec:methods:bit-basis}
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
\subsubsection{Integer Programming Mapping QUBO}
\label{sec:methods:ilp-qubo}
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
\subsubsection{Minimum Dominating Set Problem}
\label{sec:methods:mds}
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
\subsubsection{Minimum Dominating Set Qubo}
\label{sec:methods:mds-qubo}
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
\subsection{Quantum Annealing}
\label{methods:annealing}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\subsubsection{Modified annealing schedule}
\label{methods:annealing-schedule}
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
\subsection{Simulation of a Quantum Annealer}
\label{sec:methods:simulation}
%----------------------------------------------------------------------------------------

@@

%========================================================================================
\section{CONCLUSION}
%========================================================================================

@@

C.K. drank a lot of coffee.
